\section{Evaluation}

	\begin{enumerate}
	\item For a good SAMPLE of how to list the basic population (x male, y female) of the survey, have a look at paper number 25 from the Appendix. (WIP)
	\item MOTIVATE: explain why we make this field study, explain what we hope to expect. what are our assumptions. what did we expect from the questionnaires, what did we expect from the interviews?
	\end{enumerate}

	In order to see whether our thoughts regarding the survey platform hold true in practice, we chose to conduct an expert interview with two display providers and also a short field study at our university, deploying surveys to a public display and to tablets.


\subsection{Expert Interview}



\subsection{Field Study}

	The field study took place during the first two weeks of March 2015 in a faculty building of Ludwig-Maximilians-University of Munich. Data was collected on 14 consecutive days and personal semi-structured interviews were carried out on five working days during in the same two weeks. A total of 149 interactions were recorded with the game installed on the public display and 63 survey responses were recorded.

	The goal of this study was to validate the previous thoughts and to see how users use and respond to the survey platform.

\subsubsection{Research Questions}

	The research questions were:

	\begin{itemize}
	\item What motivated our users to fill out surveys?
	\item Which channels are most suited for completing surveys (on a digital platform) in public?
	\item In which situations is the user most willing to answer surveys on public displays?
	\item (not really copious: how many questions are acceptably)
	\item (not really copious: how the users noticed / perceived the survey)
	\end{itemize}

	In addition to these questions we were interested in user stories, which feedback they gave us in regards to answering surveys on screens in the public.

\subsubsection{Study Setup}

	\paragraph{Participants}

	\paragraph{Apparatus}

		Our object of investigation was a large touchscreen with four feedback channels for completing a survey.

		The survey was run on a XXXXX display . The main application installed on the public display was a game called \textit{Balloon Shooter} developed and run by Jiamin Shi, a PhD student at the Group for Media Informatics at LMU Munich.

		\begin{enumerate}
		\item list as detailed information regarding the game as possible
		\item ask Jiamin, whether I can post screenshots of the game?
		\end{enumerate}

	\paragraph{Location}

	Faculty building for computer science, ethnology, political science, japanologie and physics. m,m

	The study setup was in the entrance hall of the university building, .

	% Show Diagram of User paths inside the entrance hall.


\subsubsection{Condition}


\subsubsection{Methodology}

\subsubsection{Results}

	\begin{enumerate}
	\item describe the results from the evaluation
	\item e.g. 1) prefered feedback channel, 2) number of acceptable answers, 3) preferred setting
	\item say which implications this gives for the PDSurvey research platform
	\end{enumerate}

	\paragraph{Quantitative Data}
		asdf


	\paragraph{Qualitative Data}
		asdf


	\begin{enumerate}
	\item TODO: think about what my evaluation has to do with my platform. make sure that this link is clear! Make this link clear in the following summary.
	\end{enumerate}


\subsection{Summary}

	\begin{enumerate}
	\item (summarize the expert interviews)
	\item summarize the quantitative results
	\item summarize the qualitative results 
	\end{enumerate}